### 2018-10-13 tex/abstract.tex
Version 2.2

In large-scale data-parallel analytics, shuffle, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large overhead. Due to the dependency constrains, execution of those descendant tasks could be delayed by logy shuffles.
To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
{\color{blue}
During shuffle optimization process, we propose a performance model called \textit{Framework Resources Quantification}(FRQ) model. 
FRQ model displays utilization of resources in time dimension and calculate exectuion time of computing jobs on different DAG frameworks. 
We use FRQ model to assist in analyzing shuffle process and verify SCache shuffle optimization by mathematics.
}
By extracting and analyzing shuffle dependencies prior to the actual task execution, SCache can adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node. 
Meanwhile, SCache takes full advantage of the system memory to accelerate the shuffle process. 
% {\color{red}
% We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
% Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
% }
{\color{blue}
We have implemented SCache as the external shuffle service and co-scheduler on both Apache Spark and Apache Hadoop. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average. On Apache Hadoop, Scache optimize end-to-end Terasort completion time by 15\%.
}
\end{abstract}

>>>>

In large-scale data-parallel analytics, shuffle, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large overhead. Due to the dependency constrains, execution of those descendant tasks could be delayed by logy shuffles.
To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
{\color{blue}
During shuffle optimization process, we propose a performance model called \textit{Framework Resources Quantification}(FRQ) model. 
FRQ model displays utilization of resources in time dimension and calculate execution time of computing jobs on different DAG frameworks. 
We use FRQ model to assist in analyzing shuffle process and verify SCache shuffle optimization by mathematics.
}
By extracting and analyzing shuffle dependencies prior to the actual task execution, SCache can adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node. 
Meanwhile, SCache takes full advantage of the system memory to accelerate the shuffle process. 
% {\color{red}
% We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
% Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
% }
{\color{blue}
We have implemented SCache as the external shuffle service and co-scheduler on both Apache Spark and Apache Hadoop. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average. On Apache Hadoop, SCache optimize end-to-end Terasort completion time by 15\%.
}
\end{abstract}

### 2018-10-13 tex/evaluation.tex
Version 2.2

In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
{\color{blue}
To prove SCache compatibility as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
Due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop Mapreduce with SCache.
}
Finally, we measure the overhead of weighted reservoir sampling. 
In summary, SCache can decrease ~$89\%$ time of Spark shuffle without introducing extra network transfer.
More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying the optimization from SCache.
{\color{blue}Meanwhile, Hadoop Mapreduce with Scache optimize job completion time by up to 15\% and an average of 13\%}

@@

To prove SCache compatibility as a cross-framework plug-in, we also implemented Scache on Hadoop MapReduce as the external shuffle service and co-scheduler. Although \textit{pre-scheduling reduce tasks} is not critical for the simple DAG computing in Hadoop MapReduce, some shuffle-heavy jobs on Hadoop Madpreduce can still be optimized by SCache shuffle data management.

Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop Mapreduce running Terasort. Both figures have the same proportion of time. Hadoop MapReduce with SCache brings 15\% of total time optimization with 384GB input data size. 
As shown in the Figure \ref{fig:hadoop_terasort_origin}, Hadoop Mapreduce without SCache writes intermediate data locally in the Map phase. The shuffle phase and reduce phase start simultaneously. Because the large amount of shuffle data reaches the network bottleneck, The beginning part of reduce needs to wait needs to wait for network transfer. This causes the CPU resources to be idle. 
As shown in the Figure \ref{fig:hadoop_terasort_scache}, Hadoop Madpreduce with SCache start pre-fetching in the Map phase. This avoids the Reduce phase waiting for the shuffle data. Furthermore, pre-fetching utilize the idle IO throughput in the Map phase. As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop Mapreduce with Scache optimize Terasort overall completion time by up to 15\% and an average of 13\% with input data sizes from 128GB to 512GB.
}

>>>>

In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
{\color{blue}
To prove SCache compatibility as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
Due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop Mapreduce with SCache.
}
Finally, we measure the overhead of weighted reservoir sampling. 
In summary, SCache can decrease ~$89\%$ time of Spark shuffle without introducing extra network transfer.
More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying the optimization from SCache.
{\color{blue}Meanwhile, Hadoop Mapreduce with SCache optimize job completion time by up to 15\% and an average of 13\%}

@@

To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce as the external shuffle service and co-scheduler. Although \textit{pre-scheduling reduce tasks} is not critical for the simple DAG computing in Hadoop MapReduce, some shuffle-heavy jobs on Hadoop Madpreduce can still be optimized by SCache shuffle data management.

Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop Mapreduce running Terasort. Both figures have the same proportion of time. Hadoop MapReduce with SCache brings 15\% of total time optimization with 384GB input data size. 
As shown in the Figure \ref{fig:hadoop_terasort_origin}, Hadoop Mapreduce without SCache writes intermediate data locally in the Map phase. The shuffle phase and reduce phase start simultaneously. Because the large amount of shuffle data reaches the network bottleneck, The beginning part of reduce needs to wait needs to wait for network transfer. This causes the CPU resources to be idle. 
As shown in the Figure \ref{fig:hadoop_terasort_scache}, Hadoop Madpreduce with SCache start pre-fetching in the Map phase. This avoids the Reduce phase waiting for the shuffle data. Furthermore, pre-fetching utilize the idle IO throughput in the Map phase. As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop Mapreduce with SCache optimize Terasort overall completion time by up to 15\% and an average of 13\% with input data sizes from 128GB to 512GB.
}

### 2018-10-13 tex/intro.tex
Version 2.2

{\color{blue}
In order to visually analyze above-mentioned resources scheduling, we propose a performance model called \textit{Framework Resources Quantification}(FRQ) model. FRQ model quantifies computing and I/O resources and displays resources scheduling strategy of DAG framework in time dimension. We use FRQ model to assist in analyze the deficiencies of resources scheduling and optimize it. 
FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
According to the above five parameters and the scheduling strategy of the DAG framework, FRQ model is able to calculate the execution time of each phase of a computing job. 
Take Apache Hadoop MapReduce as a simple DAG computing example, we use FRQ to model each phases of the computing, including Map, Shuffle, and Reduce.
By revealing the relationships between the various phases, FRQ model assist us in discovering the irrationality of resource scheduling during computing.
I/O resource in Map phase is not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delay the execution time of reduce phase. 
This situation will be amplified in shuffle-sensitive tasks.
}

@@

{\color{blue}
We have implemented SCache, a customized Apache Spark \cite{apachespark} and a customized Apache Hadoop. We have also designed a performance model called \textit{Framework Resources Quantification}(FRQ) model to analyze the shuffle optimization of SCache and calculate the execution time of each phase of computing job. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop. On Apache Spark, we conduct basic test GroupByTest. We also evaluate Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling. On Apache Hadoop, we focus on Terasort benchmark. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied application scenarios. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark. On Apache Hadoop, Scache optimize end-to-end Terasort completion time by 15\%.
}

>>>>

{\color{blue}
In order to visually analyze above-mentioned resources scheduling, we propose a performance model called \textit{Framework Resources Quantification}(FRQ) model. FRQ model quantifies computing and I/O resources and displays resources scheduling strategy of DAG framework in time dimension. We use FRQ model to assist in analyze the deficiencies of resources scheduling and optimize it. 
FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
According to the above five parameters and the scheduling strategy of the DAG framework, FRQ model is able to calculate the execution time of each phase of a computing job. 
Take Apache Hadoop MapReduce as a simple DAG computing example, we use FRQ to model each phases of the computing, including Map, Shuffle, and Reduce.
By revealing the relationships between the various phases, FRQ model assist us in discovering the irrationality of resource scheduling during computing.
I/O resource in Map phase is not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
This situation will be amplified in shuffle-sensitive tasks.
}

@@

{\color{blue}
We have implemented SCache, a customized Apache Spark \cite{apachespark} and a customized Apache Hadoop. We have also designed a performance model called \textit{Framework Resources Quantification}(FRQ) model to analyze the shuffle optimization of SCache and calculate the execution time of each phase of computing job. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop. On Apache Spark, we conduct basic test GroupByTest. We also evaluate Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling. On Apache Hadoop, we focus on Terasort benchmark. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied application scenarios. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark. On Apache Hadoop, SCache optimize end-to-end Terasort completion time by 15\%.
}
